---
title: "Quik_start_for_scDrugHunter"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Quik_start_for_scDrugHunter}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Use scDGS function to calculate drug-gene pairs' DrugHunter score for candidate genes
### Prepare input for scDGS
```{r setup}
library(scDrugHunter)
```


```{r}
#Add test single-cell dataset.
test_seurat <- scDrugHunter::test_seurat

#Single cell input need cell type colname 'Cell_type' in meta.data and genes in 'gene_symbols' format
test_seurat@meta.data$Cell_type <- test_seurat@meta.data$annotation2
rownames(test_seurat@assays[['RNA']]@data) <- test_seurat@assays[["RNA"]]@meta.features[["gene_symbols"]]
test_seurat
```

```{r}
#Gene-trait correlation list need colnames 'gene' and 'cor'.
test_cor <- scDrugHunter::test_cor
colnames(test_cor) <- c('gene','cor')
head(test_cor)
```

```{r}
#eQTL-trait association significance need colnames 'gene' and 'pvalue'.
test_pvalue <- scDrugHunter::test_pvalue
head(test_pvalue)
```

```{r}
#List of candidate genes to hunt drugs.
test_genes <- scDrugHunter::test_candidate_genes$gene
head(test_genes)
```

### Calculate scDGS
```{r}
#Calculate single-cell Drug Gene Scores(scDGS) for candidate genes.
test_dg_pairs <- scDGS(seurat_obj = test_seurat, gene_cor = test_cor, gene_pvalue = test_pvalue, candidate = test_genes)
head(test_dg_pairs)
```
The results is arranged by scDGS and content rank of four input message for candidate drug-gene pairs in each cell type.

## Visualization
### Use radar plot showing top pairs' scDGS rank in a specific cell type
```{r,fig.width = 7, fig.height = 7}
#Plot top 20 drug-gene pairs in endothelial cells.
scDH_radar_plot(DG_pairs = test_dg_pairs, cell_type = 'Endothelial Cell', top = 20, unique_g = FALSE)
```

or you can unique the top genes in drug-gene pairs by set 'unique_g = TRUE'
```{r,fig.width = 7, fig.height = 7}
scDH_radar_plot(DG_pairs = test_dg_pairs, cell_type = 'Endothelial Cell', top = 20, unique_g = TRUE)
```

## Use circlize plot showing top pairs' scDGS in a specific cell type

You can set the number of top genes by 'top_g' and top drugs for each gene by 'top_d' in the circle
```{r,fig.width = 7, fig.height = 7}
#Plot top 20 genes and top 3 drugs in endothelial cells.
scDH_circlize_plot(DG_pairs = test_dg_pairs, cell_type = 'Endothelial Cell', top_g = 20,top_d = 3)
```
The colors for genes are random selected from 'rand_color()' function and the colors for drugs are set to 'grey'











